Growing libraries of concepts with wake-sleep program induction

### 2018-07-19 talk.tex
metropolis
more talk stuff

\documentclass{beamer}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
\usepackage{listings}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis \& Mathias Sabl\'e Meyer\\Joint work with: Lucas Morales, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
%\date{November 2017}

@@

\begin{frame}{DSL learning as Bayesian inference}
  \centering
  \begin{tikzpicture}
    \node[latent,align=center] (g) {DSL: \\concept library};
    \node[latent,below = of g,xshift = -2cm] (e1) {$\text{program}_1$};
    \node[latent,below = of g,xshift = 0cm] (e2) {$\text{program}_2$};
 \node[latent,below = of g,xshift = 2cm] (e3) {$\text{program}_3$};
    \node[obs,below = of e1] (x1) {$\text{task}_1$};
    \node[obs,below = of e2] (x2) {$\text{task}_2$};
    \node[obs,below = of e3] (x3) {$\text{task}_3$};
    \edge {g} {e1,e2,e3};
    \edge {e1} {x1};
    \edge {e2} {x2};
    \edge {e3} {x3};
  \end{tikzpicture}

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Based on Exploration-Compression algorithm by Eyal Dechter

  \centering\begin{tikzpicture}
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $q$};

    \draw [->,thick] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
    \draw [->,thick] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
    \draw [->,thick] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}

>>>>

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
\usepackage{listings}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis \& Mathias Sabl\'e Meyer\\Joint with: Lucas Morales, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
%\date{November 2017}

@@

\begin{frame}{DSL learning as Bayesian inference}
  \centering

\begin{tikzpicture}[scale=2,line width=1.5mm]

  \node[latent,scale=2,align=center] at (3.5,3) (dx){DSL};
  \node[ellipse,fill=white,draw=black,inner sep=1pt,
minimum size=20pt, font=\fontsize{10}{10}\selectfont, node distance=1,scale=2] at ([xshift=2cm]dx) (zp){program};
  \node[obs,scale=2] at ([xshift=2cm]zp) (xp) {task};
  \plate {}{(zp)(xp)}{};
%  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
  %% \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
%  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->] (dx.east) -- (zp.west);
  \draw [->] (zp.east) -- (xp.west);

  \end{tikzpicture}
 %%  \begin{tikzpicture}
 %%    \node[latent,align=center] (g) {DSL: \\concept library};
 %%    \node[latent,below = of g,xshift = -2cm] (e1) {$\text{program}_1$};
 %%    \node[latent,below = of g,xshift = 0cm] (e2) {$\text{program}_2$};
 %% \node[latent,below = of g,xshift = 2cm] (e3) {$\text{program}_3$};
 %%    \node[obs,below = of e1] (x1) {$\text{task}_1$};
 %%    \node[obs,below = of e2] (x2) {$\text{task}_2$};
 %%    \node[obs,below = of e3] (x3) {$\text{task}_3$};
 %%    \edge {g} {e1,e2,e3};
 %%    \edge {e1} {x1};
 %%    \edge {e2} {x2};
 %%    \edge {e3} {x3};
 %%  \end{tikzpicture}

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Combines ideas from Wake-Sleep \& Exploration-Compression algorithm by Eyal Dechter
